Insert the article title here

### 2020-07-25 tex/results.tex
polish upto grid independence

\textit{method}: The main difference between Rockstuhl simulations and ours is that they solve a 2D problem, 
while we solve a 3D model. In our case the geometry has a finite third dimension. To cope with this
we will extend the third direction considerably, and study this effect.
We compute extinction cross section (scattering plus absorption) while Rockstuhl work present only scattering. 
But since in both scattering and absorption the resonance occur at the same wavelengths, the results are 
comparable.

\textit{mesh}: Their work does not provide any details regarding the discretization of their geometries or 
parameters involved in the simulations. We performed a grid independence study to make sure that we are
solving properly the physics and minimizing errors due to discretization.

\textit{dielectric data}: The use 6H-SiC as material, and they obtained their data from a a source that we
were not able to replicate. Instead we are using experimental data for 4h-SiC that was provided to us 
via private communications.

@@

We performed a grid independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
constant electric field aligned with the z-axis.
(similar to quadratic cylinder on Fig 18 of Rockstuhl et.al). 
Due to the nature of the geometry, and its sharp edges it was challenging to see proper convergence. However,
for this type of physics, convergence has been studied in our previous work \cite{ClementiETal2019}. 
In the Figure \ref{fig:cube535} we show a grid independence study, where we go from a mesh of 15552 
triangles (density = 1.11x10$^-4$ $N/\text{\AA}$) to 19200 (density = 9.05x10$^-5$ $N/\text{\AA}$) 
triangles and the computed results do not change.

@@

It is worth noting that the extinction cross section curve in Figure \ref{fig:cube535} has extra peaks, 
compared to the results of Figure 18 on Rockstuhl, this is due to the 3D nature of our case and the sharp 
edges. This will be approach in the following results where we attempt a replication of one of teh results 
of Figure 14 of Rockstuhl work.

@@

Figure \ref{fig:AR_22_vs_norm} show the results of the extinction cross section of a SiC pillar of fixed
height ($H=950$ nm), fixed width ($W=400$) and varied length ($L=400-2800$ nm). The simulations where performed 
performed for the Long Edge orientation, meaning that the electric field is aligned with the length pillar 
when having normal incidence. (I SHOULD PROBABLY MAKE A DIAGRAM OF THIS)

>>>>

\textit{method}: The main difference between Rockstuhl simulations and ours is that they solve a 2D problem of 
full Maxwell equations, while we solve a 3D problem with the electrostatic approximation . 
We do not count with information on their code implementations, discretization schemes, or solver.  
We compute extinction cross section (scattering plus absorption) while Rockstuhl work present only scattering
cross section. But since  the variable of interest is the wavelength at which the resonance modes occur, the 
results are comparable.

\textit{mesh}: Their work does not provide any details regarding the discretization of the geometries or 
parameters involved in the simulations.
We performed a grid independence study to make sure that we are solving properly the equations and 
minimizing errors due to discretization. Rockstuhl has a 2D geometry (infinite third dimension) while we deal 
with a 3D representation of the geometry.

\textit{dielectric data}: They use 6H-SiC as material, and they obtained their data from a a source that we
were not able to replicate. Instead we are using experimental data for 4h-SiC that was provided to us 
via private communications from the authors of Ellis et al \cite{ellis2016}.

@@

We performed a grid independence study on a SiC cube of side $L=535$ nm submerged in air, under a 
constant electric field aligned with the z-axis (similar setup to quadratic cylinder on Fig 18 of 
Rockstuhl et.al)\cite{rockstuhl2005}. 
Due to the nature of the geometry and its sharp edges it was challenging to see proper convergence. However,
for this type of physics, convergence has been studied in our previous work \cite{ClementiETal2019}. (NOT SURE IF WE NEED TO MENTION THIS)
Figure \ref{fig:cube535} shows the grid independence study where we go from a mesh of 15552 
triangles (density = 1.11x10$^-4$ $N/\text{\AA}$) to 19200 (density = 9.05x10$^-5$ $N/\text{\AA}$) 
triangles, and the computed results do not change.

@@

It is worth noting that the extinction cross section curve in Figure \ref{fig:cube535} has extra peaks 
compared to the results of Figure 18 on Rockstuhl, this is due to the 3D nature of our case and the sharp 
edges, being the latest an effect also mentioned in Rockstuhl et al. results. The 3D effect will be approach
in the following results where we attempt a replication of one of teh results of Figure 14 of Rockstuhl work.

@@

Figure \ref{fig:AR_22_vs_norm} show the results of the extinction cross section of a SiC pillar of fixed
height ($H=950$ nm), fixed width ($W=400$) and varied length ($L=400-2800$ nm). The simulations where performed 
performed for the Long Edge orientation, meaning that the electric field is aligned with the length pillar 
when having normal incidence (see Figure \ref{fig:ellis_ang_inc}).
